The Mass Distribution of Stellar-Mass Black Holes

### 2010-07-19 paper.tex
Removed paper.pdf, added Jon Gair in ack.
Modified mass of GS2023.
Added new ref for GS2023, commented out high-mass systems in table.
New high-mass data in Table 1 (caption not updated yet).

\author{Will M. Farr \and Niharika Sravan \and Ilya Mandel}

@@

\author{Vicky Kalogera}

@@

 \email{vicky@northwestern.edu}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|c|c|c|l|}
      \hline
      Source & $f$ ($\Msun$) & $q$ & $i$ (degrees) & References \\
      \hline \hline
      GRS 1915 & $N(9.5, 3.0)$ & $N(0.0857, 0.0284)$ & $N(70, 2)$ &
      \citet{Greiner2001} \\
      XTE J1118 & $N(6.44, 0.08)$ & $N(0.0264, 0.004)$ & $N(68, 2)$ &
      \citet{Gelino2008} \\ & & & & \citet{Harlaftis2005} \\
      Cyg X1 & $N(0.251, 0.007)$ & $N(2.778, 0.386)$ & $I(23, 38)$ &
      \citet{Gies2003} \\ 
      XTE J1650 & $N(2.73, 0.56)$ & $U(0, 0.5)$ & $I(50, 80)$ &
      \cite{Orosz2004} \\
      GRS 1009 & $N(3.17, 0.12)$ & $N(0.137, 0.015)$ & $I(37, 80)$ &
      \cite{Filippenko1999} \\
      M33 X7 & $N(0.46, 0.08)$ & $N(4.47, 0.61)$ & $N(74.6, 1)$ &
      \citet{Orosz2007} \\
      A0620 & $N(2.76, 0.036)$ & $N(0.06, 0.004)$ & $N(50.98, 0.87)$ &
      \citet{Cantrell2010} \\ & & & & \citet{Neilsen2008} \\
      GRO J0422 & $N(1.13, 0.09)$ & $U(0.076, 0.31)$ & $N(45, 2)$ &
      \citet{Gelino2003} \\
      Nova Mus 1991 & $N(3.01, 0.15)$ & $N(0.128, 0.04)$ & $N(54,1.5)$
      & \cite{Gelino2001} \\
      GRO J1655 & $N(2.73,0.09)$ & $N(0.3663, 0.04025)$ & $N(70.2,
      1.9)$ & \citet{Greene2001} \\
      4U 1543 & $N(0.25, 0.01)$ & $U(0.25, 0.31)$ & $N(20.7,1.5)$ & 
      \citet{Orosz2003} \\
      XTE J1550 & $N(7.73,0.4)$ & $U(0,0.04)$ & $N(74.7, 3.8)$ &
      \citet{Orosz2010} \\
      V4641 Sgr & $N(3.13,0.13)$ & $U(0.42,0.45)$ & $N(75,2)$ &
      \citet{Orosz2003} \\
      GS 2023 & $N(6.08, 0.06)$ & $U(0.056,0.063)$ & $N(55,4)$ &
      \citet{Charles2006} \\
      GS 1354 & $N(5.73, 0.29)$ & $N(0.12,0.04)$ & $I(50, 80)$ & 
      \citet{Casares2009} \\
      Nova Oph 77 & $N(4.86,0.13)$ & $U(0, 0.053)$ & $I(60, 80)$ &
      \citet{Charles2006} \\
      GS 2000 & $N(5.01, 0.12)$ & $U(0.035, 0.053)$ & $I(43, 74)$ &
      \citet{Charles2006} \\
      \hline
    \end{tabular}
  \end{center}
  \caption{\label{tab:sources} The source parameters for the 17 low
    mass X-ray binaries used in this work.  $f$ is the mass function for
    the compact object, $q$ is the mass ratio $M_2/M$, and $i$ is the
    inclination of the system to the line of sight.  We indicate the
    distribution used for the true parameters when computing the
    probability distributions for the masses of these systems:
    $N(\mu,\sigma)$ implies a Gaussian with mean $\mu$ and standard
    deviation $\sigma$, $U(a,b)$ is a uniform distribution between $a$ and
    $b$, and $I(\alpha,\beta)$ is an isotropic distribution between the
    angles $\alpha$ and $\beta$.  \fixme{Orosz for XTE J1550 needs a
      real reference \citep{Orosz2010}.}} 
\end{table}

@@

In Figure \ref{fig:alpha}, we display a histogram of the resulting
samples in $\alpha$; this represents the one-dimensional
``marginalized'' distribution
\begin{equation}
  \label{eq:alpha-pdf}
  p(\alpha|d) = \int d\Mmin\, d\Mmax\, p(\{\Mmin, \Mmax, \alpha\}|d).
\end{equation}
The resulting distribution is quite broad with 
\begin{equation}
  -7.66 < \alpha < -1.36
\end{equation}
enclosing 90\% of the probability.  The median value is $\alpha =
-4.28$, and we have $\alpha < 0$ (a falling underlying mass
distribution) at 98.7\% confidence.  The distribution of the minimum
mass is also quite interesting, but we defer this discussion until
Section \ref{sec:minimum-mass}, where we discuss the distribution for
the minimum black hole masses in the context of all our models.

\begin{figure}
  \begin{center}
    \plotone{plots/alpha}
  \end{center}
  \caption{\label{fig:alpha} A histogram of the MCMC samples for
    $\alpha$ from the power-law distribution defined in Equation
    \eqref{eq:power-law-dist}.  The histogram is an approximation to
    the one-dimensional marginalized PDF in Equation
    \eqref{eq:alpha-pdf}.  The favored value is near $\alpha = -4$.
    The fraction of the distribution with $\alpha < 0$ is 98.7\%.  The
    5\% quantile is $-7.66$, the median is $-4.28$, and the 95\%
    quantile is $-1.36$.}
\end{figure}

@@

Figure \ref{fig:exp-M0} displays the marginalized posterior
distribution for the scale mass of the exponential, $M_0$.  The median
scale mass is $M_0 = 3.00$, and $1.57 \leq M_0 \leq 5.71$ with 90\%
confidence.  We defer discussion of the distribution of $\Mmin$ until
Section \ref{sec:minimum-mass}.  Refer to Figure \ref{fig:dists}
for the resulting shape of the distribution of distributions.

\begin{figure}
  \begin{center}
    \plotone{plots/exp-M0}
  \end{center}
  \caption{\label{fig:exp-M0} The distribution of scale masses, $M_0$,
    measured in units of a solar mass for the exponential underlying
    mass distribution defined in Equation \eqref{eq:exp-def}.  The
    median scale mass is $M_0 = 3.00$; with 90\% confidence $1.57 \leq
    M_0 \leq 5.71$. }
\end{figure}

@@

This work was supported by grant \fixme{XXX}.  Calculations for this
work were performed on the Northwestern Fugu cluster, which was
partially funded by NSF MRI grant \fixme{XXX}.

>>>>

\author{Will M. Farr \and Niharika Sravan}

@@

\author{Ilya Mandel \and Vicky Kalogera}

@@

 \email{ilyamandel@chgk.info, vicky@northwestern.edu}

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|c|c|c|l|}
      \hline
      Source & $f$ ($\Msun$) & $q$ & $i$ (degrees) & References \\
      \hline \hline
      GRS 1915 & $N(9.5, 3.0)$ & $N(0.0857, 0.0284)$ & $N(70, 2)$ &
      \citet{Greiner2001} \\
      XTE J1118 & $N(6.44, 0.08)$ & $N(0.0264, 0.004)$ & $N(68, 2)$ &
      \citet{Gelino2008} \\ & & & & \citet{Harlaftis2005} \\
      XTE J1650 & $N(2.73, 0.56)$ & $U(0, 0.5)$ & $I(50, 80)$ &
      \cite{Orosz2004} \\
      GRS 1009 & $N(3.17, 0.12)$ & $N(0.137, 0.015)$ & $I(37, 80)$ &
      \cite{Filippenko1999} \\
      A0620 & $N(2.76, 0.036)$ & $N(0.06, 0.004)$ & $N(50.98, 0.87)$ &
      \citet{Cantrell2010} \\ & & & & \citet{Neilsen2008} \\
      GRO J0422 & $N(1.13, 0.09)$ & $U(0.076, 0.31)$ & $N(45, 2)$ &
      \citet{Gelino2003} \\
      Nova Mus 1991 & $N(3.01, 0.15)$ & $N(0.128, 0.04)$ & $N(54,1.5)$
      & \cite{Gelino2001} \\
      GRO J1655 & $N(2.73,0.09)$ & $N(0.3663, 0.04025)$ & $N(70.2,
      1.9)$ & \citet{Greene2001} \\
      4U 1543 & $N(0.25, 0.01)$ & $U(0.25, 0.31)$ & $N(20.7,1.5)$ & 
      \citet{Orosz2003} \\
      XTE J1550 & $N(7.73,0.4)$ & $U(0,0.04)$ & $N(74.7, 3.8)$ &
      \citet{Orosz2010} \\
      V4641 Sgr & $N(3.13,0.13)$ & $U(0.42,0.45)$ & $N(75,2)$ &
      \citet{Orosz2003} \\
      GS 2023 & $N(6.08, 0.06)$ & $U(0.056,0.063)$ & $I(66, 70)$ &
      \citet{Charles2006} \\
      & & & & \citet{Khargharia2010} \\
      GS 1354 & $N(5.73, 0.29)$ & $N(0.12,0.04)$ & $I(50, 80)$ & 
      \citet{Casares2009} \\
      Nova Oph 77 & $N(4.86,0.13)$ & $U(0, 0.053)$ & $I(60, 80)$ &
      \citet{Charles2006} \\
      GS 2000 & $N(5.01, 0.12)$ & $U(0.035, 0.053)$ & $I(43, 74)$ &
      \citet{Charles2006} \\
      \hline \hline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% High Mass Follows
      Cyg X1 & $N(0.251, 0.007)$ & $N(2.778, 0.386)$ & $I(23, 38)$ &
      \citet{Gies2003} \\ 
      M33 X7 & $N(0.46, 0.08)$ & $N(4.47, 0.61)$ & $N(74.6, 1)$ &
      \citet{Orosz2007} \\
      NGC 300 X1 & $N(2.6, 0.3)$ & $U(1.05, 1.65)$ & $I(60, 75)$ &
      \citet{Crowther2010} \\
      LMC X1 & $N(0.148, 0.004)$ & $N(2.91, 0.49)$ & $N(36.38, 2.02)$
      & \citet{Orosz2009} \\
      IC 10 X1 & $N(7.64, 1.26)$ & $U(0.7, 1.7)$ & $I(75, 90)$ & 
      \citet{Prestwich2007} \\
       & & & & \citet{Silverman2008} \\
       \hline
    \end{tabular}
  \end{center}
  \caption{\label{tab:sources} The source parameters for the 17 low
    mass X-ray binaries used in this work.  $f$ is the mass function for
    the compact object, $q$ is the mass ratio $M_2/M$, and $i$ is the
    inclination of the system to the line of sight.  We indicate the
    distribution used for the true parameters when computing the
    probability distributions for the masses of these systems:
    $N(\mu,\sigma)$ implies a Gaussian with mean $\mu$ and standard
    deviation $\sigma$, $U(a,b)$ is a uniform distribution between $a$ and
    $b$, and $I(\alpha,\beta)$ is an isotropic distribution between the
    angles $\alpha$ and $\beta$.  \fixme{Orosz for XTE J1550 needs a
      real reference \citep{Orosz2010}.}} 
\end{table}

@@

In %Figure \ref{fig:alpha}
, we display a histogram of the resulting
samples in $\alpha$; this represents the one-dimensional
``marginalized'' distribution
\begin{equation}
  \label{eq:alpha-pdf}
  p(\alpha|d) = \int d\Mmin\, d\Mmax\, p(\{\Mmin, \Mmax, \alpha\}|d).
\end{equation}
The resulting distribution is quite broad with 
\begin{equation}
  -7.66 < \alpha < -1.36
\end{equation}
enclosing 90\% of the probability.  The median value is $\alpha =
-4.28$, and we have $\alpha < 0$ (a falling underlying mass
distribution) at 98.7\% confidence.  The distribution of the minimum
mass is also quite interesting, but we defer this discussion until
Section \ref{sec:minimum-mass}, where we discuss the distribution for
the minimum black hole masses in the context of all our models.

% \begin{figure}
%   \begin{center}
%     \plotone{plots/alpha}
%   \end{center}
%   \caption{\label{fig:alpha} A histogram of the MCMC samples for
%     $\alpha$ from the power-law distribution defined in Equation
%     \eqref{eq:power-law-dist}.  The histogram is an approximation to
%     the one-dimensional marginalized PDF in Equation
%     \eqref{eq:alpha-pdf}.  The favored value is near $\alpha = -4$.
%     The fraction of the distribution with $\alpha < 0$ is 98.7\%.  The
%     5\% quantile is $-7.66$, the median is $-4.28$, and the 95\%
%     quantile is $-1.36$.}
% \end{figure}

@@

%Figure \ref{fig:exp-M0}
 displays the marginalized posterior
distribution for the scale mass of the exponential, $M_0$.  The median
scale mass is $M_0 = 3.00$, and $1.57 \leq M_0 \leq 5.71$ with 90\%
confidence.  We defer discussion of the distribution of $\Mmin$ until
Section \ref{sec:minimum-mass}.  Refer to Figure \ref{fig:dists}
for the resulting shape of the distribution of distributions.

% \begin{figure}
%   \begin{center}
%     \plotone{plots/exp-M0}
%   \end{center}
%   \caption{\label{fig:exp-M0} The distribution of scale masses, $M_0$,
%     measured in units of a solar mass for the exponential underlying
%     mass distribution defined in Equation \eqref{eq:exp-def}.  The
%     median scale mass is $M_0 = 3.00$; with 90\% confidence $1.57 \leq
%     M_0 \leq 5.71$. }
% \end{figure}

@@

This work was supported by grant \fixme{XXX}.  Calculations for this
work were performed on the Northwestern Fugu cluster, which was
partially funded by NSF MRI grant \fixme{XXX}.  We thank Jonathan Gair
for helpful discussions.
